\begin{thebibliography}{9}
\bibitem{MDBtoV}
Shibata, S., Nakata, A., Hashimoto, T., "Evaluation Of Moving Progressive Deformable Barrier Test Method By Comparing Car to Car Crash Test", Honda R\&D Co., Ltd. Automobile R\&D Center,  \url{https://pdfs.semanticscholar.org/82e9/9f428afe1d61e81e54248d95e8e486c9f3c1.pdf}.

\bibitem{plascore}
Offial website of Plascore Incorporated, \url{https://www.plascore.com}

\bibitem{mohrdoyoyo2003}
Mohr, D., Doyoyo, M., "Nucleation and propagation of plastic collapse bands in aluminum honeycomb." In: \textit{Journal of Applied Physics}, 94(4):2262-2270, 2003.

\bibitem{mohrdoyoyo2004a}
Mohr, D., Doyoyo, M., "Large plastic deformation of metallic honeycomb: Orthotropic rate-independent constitutive model." In: \textit{International Journal of Solids and Structures}, 41(16-17):4435–4456, 2004.

\bibitem{mohrdoyoyo2004b}
Mohr, D., Doyoyo, M., "Experimental Investigation on the Plasticity of Hexagonal Aluminum Honeycomb Under Multiaxial Loading." In: \textit{Journal of Applied Mechanics}, Vol 71:4435–4456, 2004.

\bibitem{mohrdoyoyo2004c}
Mohr, D., Doyoyo, M., "Deformation-induced folding systems in thin-walled monolithic hexagonal metallic honeycomb." In: \textit{International Journal of Solids and Structures}, 41 (2004) 3353-3377.

\bibitem{niedermeyer}
Niedermeyer, S., "Charakterisierung und Modellierung von Crash-Barrieren aus Aluminiumwabenstrukturen." Technical report, Fraunhofer-Institut für Kurzzeit-dynamik, Ernst-Mach-Institut, Freiburg, 2007.

\bibitem{weerts}
Weerts, R.A.J., "Towards improved modeling of the oblique moving deformable barrier." Technical report, Eindhoven University of Technology, 2016.

\bibitem{popp}
Popp, A., "Modellbildung von Crashbarrieren und Entwicklung einer Honeycomb- Materialformulierung." Technical report, Technische Universät München, 2007.

\bibitem{DAP}
Van Iersel, D.A.P., "Modeling of aluminium honeycomb crushing using a homogenised non-local continuum model." Technical report, Eindhoven University of Technology, 2018.

\bibitem{geers4mm10}
Geers, M., "Advanced Computational Continuum Mechanics, Part I: Continuum Mechanics Theory, Lecture notes for course 4MM10", Eindhoven University of Technology.

\bibitem{compmethodsplasticity}
De Souza Neto, E.A., Peric, D., Owen, D.R.J., "Computational Methods for Plasticity: Theory and Applications". 2008, Chapter 14.

\bibitem{chaves}
Chaves, Eduardo W. "Notes on Continuum Mechanics." (2013) 10.1007/978-94-007-5986-2. 

\bibitem{Lee}
Lee, E.H., "Elastic-Plastic Deformation at Finite Strains." In: \textit{Journal of Applied Mechanics}, Vol: 36, 1969.

\end{thebibliography}